---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BIT's data analysis toolbox

This repository is a collection of R scripts and functions, implementing common data analysis tasks at BIT's Predictiv team. It is heavily focused on functionality that is used to analyze data from Predictiv surveys. Though we are generally open to contributions (see "Contributing" sections), they should be in line with the package's scope. Pull requests and feature requests that are out of scope (e.g., niche and/or one-off analyses) will be rejected.

All analysis and parameter defaults were chosen based on the recommendations given in the Blue Book v1.5.

## Features

An graphical overview of the package can be found under `doc/architecture-diagram`.

The following modules are currently implemented

-   **Data loading** module: load data from a local `csv` file, pull data from a remote `DuckLake` database
-   **Data cleaning** template: template with common data cleaning routines; as per the wish of researchers, this is not formally part of the package and has to be adapted manually for each survey. It is kept in this repo for version control and exposure

# Getting started

## Installation

You can install the development version of bittoolbox from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("BehaviouralInsights/data-analysis-toolbox")
```

## Example

This is a basic example for an end-to-end analysis pipeline, using functions, bundled with this package:

```{r example}
library(bittoolbox)

# Note: templates are not ready for consumption, but have to be adjusted by the user for their specific use case (adjusting variable names, toggling analysis steps, etc.) after calling `use_template`. Templates only provide a scaffold
bittoolbox::use_template("predictiv_cint_cleaning") # Copy BIT UKs data cleaning template to working directory

data <- bittoolbox::ai_can_take_your_job_not_mine # Load bundled example data
```

# Contributing

For features requests, bug reports, etc., please use the `Issues` tab in the repository. This is the preferred way to contribute to this package.

Please note though that this only applies to core-functionality of the package: bundled templates are not covered by this, and are **not** maintained by the maintainers of this repo. If you want to change an existing template, please create a PR (see below); If you want to make a suggestion for a new template to be bundled, please open an issue and link to the files you want to bundle with this package.

Another (optional and more involved) way to contribute is to contribute your own custom functions. To do this, please branch off `main` and create a feature branch. Once you are done, create a pull request and tag the package maintainer as reviewer. **You won't be able to directly commit to `main` or merge without review/approval of your PR.**
