---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# BIT's data analysis toolbox

This repository is a collection of R scripts and functions, implementing common data analysis tasks at BIT's Predictiv team. It is heavily focused on functionality that is used to analyze data from Predictiv surveys. Though we are generally open to contributions (see "Contributing" sections), they should be in line with the package's scope. Pull requests and feature requests that are out of scope (e.g., niche and/or one-off analyses) will be rejected.

All analysis and parameter defaults were chosen based on the recommendations given in the Blue Book v1.5.

## Features

An graphical overview of the package can be found under `doc/architecture-diagram`.

The following modules are currently implemented

-   **Data loading** module: load data from a local `csv` file, pull data from a remote `DuckLake` database
-   **Data cleaning** template: template with common data cleaning routines; as per the wish of researchers, this is not formally part of the package and has to be adapted manually for each survey. It is kept in this repo for version control and exposure

# Getting started

## Installation

You can install the development version of bittoolbox from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("BehaviouralInsights/data-analysis-toolbox")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(bittoolbox)

PATH_TO_DATA = './my_data_path/my_data.csv'

# data <- import_from_file(PATH_TO_DATA) # Load example data
use_template() # Copy default data cleaning template working directory
```

# Contributing

For features requests, bug reports, etc., please use the `Issues` tab in the repository. This is the preferred way to contribute to this package.

Another (optional and more involved) way to contribute is to contribute your own custom functions. To do this, please branch off `main` and create a feature branch. Once you are done, create a pull request and tag the package maintainer as reviewer. **You won't be able to directly commit to `main` or merge without review/approval of your PR.**
